### 2013-09-26 Paper_Markdown.Rmd
Modified plotting for figures in the markdown text.

ggplot(dissim.scores) + 
  geom_density(aes(x = dissim, fill=class), alpha=0.5) +
  #facet_wrap(~class, scales='free') +
  theme_bw() +
  theme(text = element_text(size=24, family='serif'))

@@

ggplot(data = mds, aes(x = X1, y = X2)) +
  geom_point(alpha=0.5, size = 4, aes(color = non.ana)) + theme_bw() +
  xlab('MDS Axis One') + ylab('MDS Axis Two') +
    theme(text = element_text(size=24, family='serif'))

>>>>

ggplot(dissim.scores) + 
  geom_density(aes(x = dissim, fill=class), alpha=0.5) +
  #facet_wrap(~class, scales='free') +
  theme_bw() +
  theme(text = element_text(size=24, family='serif')) +
  scale_x_sqrt()

@@

non.ana <- ggplot(data = mds, aes(x = X1, y = X2)) +
  geom_point(alpha=0.5, size = 4, aes(color = non.ana)) +   
  theme_bw() +
  xlab('MDS Axis One') + ylab('MDS Axis Two') +
  theme(text = element_text(size=24, family='serif'))

non.ana.map <- ggplot(data = data.frame(map), aes(long, lat)) + 
  geom_path(aes(group=group), color='black') +
  geom_point(data = data.frame(climate), 
             aes(x = LONDD, y = LATDD, color = mds$non.ana)) +
  coord_map(xlim=c(-170, -40), ylim=c(21, 83))
